Modeling memory and taxis to analyze migrations

### 2021-01-13 code/StrategicVsTactical_PartI_v2.Rmd
Changes to match dx and world

For reference and replicability, I include the incrementally constructed R code, which relies heavily on the `deSolve` (Soetaert et al. 2010) and `ReacTran` (Soetaert and Filip, 2020) packages, which efficiently implement transport ODE and PDE systems in R.

@@

parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2, lambda = 0)

@@

```{r resourceOnly, fig.height = 5, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 5e2, beta = 0, lambda = 0, dx = dx)

@@

```{r resourceAndMemory, fig.height = 5, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 3e2, beta = 3e2, lambda = 0, dx = dx)

@@

```{r exampleResourcePlots, fig.width = 10, fig.height = 6}
source("functions.R")
Time <- 1:100; X <- 0:100

@@

```{r PulseSim1, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 0, beta = 4e2, lambda = 0, dx = dx)
Memory_PulsedResource_Sim <- runManyYears(pop.Year1, Time, 
                                  Resource = R1, Parameters = parameters, n.years = 6)
par(mfrow = c(1,2), oma = c(0,0,3,0))
plotYearList(Memory_PulsedResource_Sim, tau = tau)
plotYearList(Memory_PulsedResource_Sim, tau = tau, persp = TRUE, scale = FALSE, expand = 100)
title(printParameters(parameters), outer = TRUE)
```

>>>>

For reference and replicability, I include the incrementally constructed R code, which relies heavily on the `deSolve` (Soetaert et al. 2010) and `ReacTran` (Soetaert and Filip, 2010) packages, which efficiently implement transport ODE and PDE systems in R.

@@

parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2)

@@

```{r resourceOnly, fig.height = 5, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 5e2, beta0 = 0, beta1 = 0)

@@

```{r resourceAndMemory, fig.height = 5, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 3e2, beta0=20, beta1 = 5e2)

@@

```{r exampleResourcePlots, fig.width = 10, fig.height = 6}
source("functions2.R")
Time <- 1:100; X <- 0:100

@@

```{r PulseSim1, fig.width = 10}
parameters <- c(epsilon = 5, alpha = 0, beta0 = 20, beta1 = 5e2)
Memory_PulsedResource_Sim <- runManyYears(pop.Year1, Time, Resource = R1, Parameters = parameters, n.years = 6)
